Acoustic Scene Classification: \\ Supervised and Unsupervised Approaches using the Scattering Transform

### 2016-06-23 paper/structureScene.tex
transitions
some elements on time-frequency scattering

\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,positioning}
\usepackage{url}
\usepackage{color}
\usepackage{graphicx}
\usepackage{xspace}
\newcommand*{\eg}{e.g.\@\xspace}
\newcommand*{\ie}{i.e.\@\xspace}

@@

The scattering transform is defined mathematically as an infinite cascade of nonlinear layers, each consisting of a wavelet transform modulus operator.
In practice, to achieve invariance to translation up to $T = 186\,\mathrm{ms}$, \ie of the order of the minimal duration between non-overlapping acoustic events, two layers of scattering transform of the audio signal $\boldsymbol{x}(t)$ suffice.
The next section describes the operations involved in temporal scattering.

@@

\subsection{Time-frequency scattering}
\cite{Anden2015}

@@

>>>>

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,positioning}
\usepackage{url}
\usepackage{color}
\usepackage{graphicx}
\usepackage{xspace}
\newcommand*{\eg}{e.g.\@\xspace}
\newcommand*{\ie}{i.e.\@\xspace}

@@

The scattering transform is defined mathematically as an infinite cascade of nonlinear layers, each consisting of a wavelet transform modulus operator.
In practice, to achieve invariance to translation up to $T = 186\,\mathrm{ms}$, \ie of the order of the minimal duration between non-overlapping acoustic events, two layers of scattering transform of the audio signal $\boldsymbol{x}(t)$ suffice.
The next subsection describes the operations involved in temporal scattering.

@@

The next subsection extends the second-order scattering operator to joint wavelet transforms over the time and log-frequency variables.

\subsection{Time-frequency scattering}

\cite{Anden2015}
%The temporal scale $2^{\gamma_2}/\xi_2$ takes $5$ values between $23\,\mathrm{ms}$ and $370\,\mathrm{ms}$.
%The log-frequential scale $\beta$ takes $5$ values between $1/4^{\mathrm{th}}$ of an octave and $4$ octaves, as well as their $5$ "mirror" frequencies,
%according to a geometric sequence.
%In addition, the edge case $\gamma_{\mathrm{fr}} = \infty$ corresponds
%to a log-frequential low-pass filter along $4$ octaves
%according to all $5$ temporal scales $2^{\gamma_2}/\xi_2$.

@@

\subsection{}

\begin{equation}
\widetilde{\mathbf{S}}\boldsymbol{X}(\gamma, n) =
\dfrac{\log \mathbf{S}\boldsymbol{X}(\gamma, n) -
\mathbb{E}[\log \mathbf{S}\boldsymbol{X}(\gamma)]}{\sigma(\log \mathbf{S}\boldsymbol{X}(\gamma))}
\end{equation}
where $\mathbb{E}[\log \mathbf{S}\boldsymbol{X}(\gamma)] = \frac{1}{N} \sum_{n=1}^{N} \log \mathbf{S}\boldsymbol{X}(\gamma,n)$ is the expected value of $\log \mathbf{S}\boldsymbol{X}(\gamma,n)$ and
\begin{equation}
\sigma(\log \mathbf{S}\boldsymbol{X} (\gamma)) =
\frac{1}{N-1} \sum_{n=1}^{N}
( \log \mathbf{S}\boldsymbol{X}(\gamma,n) - \mathbb{E}[\log \mathbf{S}\boldsymbol{X}] )
\end{equation}
 is the sample standard deviation.
